### 2015-02-23 replication_report.Rmd
created RMarkdown file created

---
title: "replication_report"
author: "Yari"
date: "February 22, 2015"
output: html_document
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2015-02-23 replication_report.Rmd
added demo script for moderation analysis and simple ggplot2 graphs. have not yet plugged in variables.

@@
 title: "replication_report"
-author: "Yari"
+author: "Yari & Kyonne"
 date: "February 22, 2015"
@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+Plan for replication project
+(1) power analyses - with and without outliers
+(2) moderation analysis by gender
+(3) graph the results with ggplot2
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+1: Get data
+```{r}
+#load packages:
+library(pwr)
+library(dplyr)
+library(plyr)
+library(ggplot2)
+library(MBESS)
+library(psych)
+library(car)
+library(lsr)
 
-```{r}
-summary(cars)
+#load data:
+dat <- read.csv("GORN_study3.csv", header = TRUE)
+head(dat)
+View(dat)
+
+#center predictor variable (using blanks for variable name until we get the translated documents:
+dat$X.center<-scale(dat$X, center=TRUE, scale=FALSE)
+
+#set moderator as a factor
+dat$M<-as.factor(dat$M)
+
+#Test for homogeneity of variance:
+leveneTest(dat$X ~ dat$M, center = mean)
+
+#simple effect of centered predictor on Y
+model.centered<-lm(dat$______ ~ dat$______.center)
+summary(model.centered)
+
+#centered models:
+m1.cent<-lm(dat$Y ~ dat$X.center 
+            + dat$M)
+summary(m1.cent)
+
+m2.cent<-lm(dat$Y ~ dat$X.center 
+            + dat$M
+            + (dat$X.center*dat$M))
+summary(m2.cent)
+
+#compare models
+anova(m1.cent, m2.cent)
+
 ```
 
-You can also embed plots, for example:
+Graph results of moderation analysis
 
 ```{r, echo=FALSE}
-plot(cars)
+##Scatterplots
+graph.simple = ggplot(dat, aes(x = wmc.center, y = stroop.rt)) 
+graph.simple + geom_smooth(method = "lm") +
+  geom_point() +
+  ggtitle("Simple Effect of Working Memory on Stroop Performance (RT)") +
+  ylab("Stroop RT") +
+  xlab("Working Memory Deviation Score from Mean")
+
+graph.moderator = ggplot(dat, aes(x = X.center, y = Y, colour = M)) 
+graph.moderator + geom_smooth(method = "lm") +
+  geom_point() +
+  ggtitle("Working Memory on Stroop Performance (RT)") +
+  ylab("Stroop RT") +
+  xlab("Working Memory Deviation Score from Mean")
 ```

### 2015-03-15 replication_report.Rmd
making a commit so that Yari can see this RMD
Layout of intentions for entire project timeline

@@
 Plan for replication project
-(1) power analyses - with and without outliers
+(1) Showing abbreviated version of the table 
+(2) Explain what that table displays 
+(3) R code to get there
+----
+Plan for added components for replication project (due later)
+(1) power analyses - with and without excluded participants
 (2) moderation analysis by gender
@@
 
-1: Get data
+3: R code
 ```{r}
@@
 dat <- read.csv("GORN_study3.csv", header = TRUE)
+dat <- tbl_df(dat)
 head(dat)
-View(dat)
+#View(dat)
+
+??describe()
 

### 2015-03-15 working-document-notes.R
Polished Replication Report .rmd document by adding space for code producting the table, explanations of analyses & code for chi-square and power analyses.
Modified Replication Reprt .rmd document by placing notes formally there (but not a part of Phase 1) into a Working Document script

@@ -1,28 +1,24 @@
 ---
-title: "Replication Report"
+  title: "replication report" <-- Our Working Document/ideas for extensions
 author: "Yari & Kyonne" 
-date: "March 15, 2015"
+date: "February 22, 2015"
 output: html_document
 ---
-
-Structure of Report: 
-(1) Display reproduced table for Study 3 results 
+  
+  Plan for replication project
+(1) Showing abbreviated version of the table 
 (2) Explain what that table displays 
-(3) R code
+(3) R code to get there
+----
+  Plan for added components for replication project (due later)
+(1) power analyses - with and without excluded participants
+(2) moderation analysis by gender
+(3) graph the results with ggplot2
 
+##In order to not show table, {r, eval = FALSE}
+##In order to not show code, {r, echo = FALSE}
 
 3: R code
-```{r, echo = FALSE}
-
-#(1) CODE FOR TABLE ONLY GOES HERE: <---delete this.
-
-```
-
-(2) Explanation: 
-The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions in Study 3. Note that at the bottom of the table is also the chi-square statistic, p-value and effect size (phi) for the data, indicating a medium-sized effect of music condition on pen choice. The table also demonstrates that the frequency of choice in the Disliked Music condition was in the hypothesized direction: Subjects tended to choose the non-advertised pen when made to listen to disliked music in an advertisement.
-
-Note that the data represented above follows the exclusion criteria set forth in the published article. Specifically, any subjects who had participated in a prior version of the study were excluded (two subjects). In addition, 19 subjects were excluded for their so-called "deviant music evaluations". These subjects were foundd to either somewhat dislike the "liked music" (music attiude score below 3) or somewhat like the "disliked music" (music attitude score above 3).
-
 ```{r, eval= FALSE}
 # (3) Code for analyses & table:
 
@@ -72,6 +68,12 @@ pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)
[…]

### 2015-03-15 working-document-notes.R
Amended the Working Document/Notes for the project

@@ -1,7 +1,7 @@
 ---
   title: "replication report" <-- Our Working Document/ideas for extensions
 author: "Yari & Kyonne" 
-date: "February 22, 2015"
+date: 
 output: html_document
 ---
   

### 2015-03-16 working-document-notes.R
got the frequencies and percentages to appear separately using prop.table, but now trying to make a nice table

@@ -79,20 +79,20 @@ pwr.chisq.test(w = NULL, N = 91, df = 1, sig.level = 0.05, power = .8)
 # Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:
 
 # Find Cronbach's Alpha for music attitudes scale (for comparison with article):
-#dat_music <- dat_e %>%
-#  select(att_muz1, att_muz2, att_muz3)
-#View(dat_music)
-#alpha(dat_music, na.rm = TRUE, delete=TRUE)
+# dat_music <- dat_e %>%
+# select(att_muz1, att_muz2, att_muz3) 
+# View(dat_music)
+# alpha(dat_music, na.rm = TRUE, delete=TRUE)
 
 #Find mean attitudes for each music condition (for comparison with article): 
-#dat_e %>%
-#  group_by(music) %>%
-#  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))
+dat_e %>%
+ group_by(music) %>%
+summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))
 
 # Add mean attitude column to dataframe:
 dat_e <- dat_e %>%
   mutate(avg_att_muz = (att_muz1 + att_muz2 + att_muz3) / 3)
-#View(dat_e)
+View(dat_e)
 
 #Check that means (for comparison with article):
 #dat_e %>%
@@ -102,7 +102,7 @@ dat_e <- dat_e %>%
 # Exclude when average attitude > 3 in disliked cond. or average attitude <3 for liked cond. (1 == liked music, 2 == disliked music)
 dat_egood <- dat_e %>%
   filter(music == 1 & avg_att_muz > 3 | music == 2 & avg_att_muz < 3)
-#View(dat_egood)
+View(dat_egood)
 
 ## Redo Chi-Square with subsetted data:
 
@@ -132,12 +132,52 @@ pwr.chisq.test(w = NULL, N = 72, df = 1, sig.level = 0.05, power = .8)
 # chisq.test(tbl2, simulate.p.value = TRUE)
 
 # CODE FOR TABLE HERE:
+install.packages("tables")
+library(tables)
+install.packages("mosaic")
+library(mosaic)
+install.packages("stargazer")
+library(stargazer)
+install.packages("xtable")
+library(xtable)
 
+
+# using tables function, doesnt work as planned
[…]

### 2015-03-27 working-document-notes.R
This is where I had done all the work. not the Rmd file

@@ -143,8 +143,15 @@ library(xtable)
 
 
 # using tables function, doesnt work as planned
-(tabular(dat_egood$music ~ (n=1) + Format(digits=2)* 
-          (dat_egood$chose_advertised_pen)* (n), data=dat_egood)))
+csvtable<-tbl_df("Experiment3_ReplicationTable_csv.csv")
+view(csvtable)
+
+
+
+
+tabular(dat_egood$music + 1) ~ (n+1) + Format(digits=2)* 
+          (dat_egood$chose_advertised_pen)* (n+ proportions), data=dat_egood)))
+
 
 #not what expected
 mosaicplot(freqtable)
@@ -153,11 +160,14 @@ mosaicplot(freqtable)
 attach(dat_egood)
 freqtable<-table(dat_egood$music,dat_egood$chose_advertised_pen)
 freqtable
-margin.table(freqtable, 0)
 margin.table(freqtable, 1)
+margin.table(freqtable, 2)
 prop.table(freqtable)
-prop.table(freqtable, 0)
-prop.table(freqtable, 1)
+proportions <-prop.table(freqtable, 1)
+proportions
+prop.table(freqtable, 2)
+
+
 
 # trying stargazer... no good
 stargazer(dat_egood[c("")], type= "text", title= "Frequencies...", digits=2, out="freqtable.txt")

### 2015-03-28 replication_report.Rmd
Add work to Rmd file

--- 2015-02-23 replication_report.Rmd
@@
 dat <- read.csv("GORN_study3.csv", header = TRUE)
-head(dat)
+dat <-tbl_df(dat)
 View(dat)
+dat %>%
+  filter(na.rm=TRUE) %>%
+  group_by(Groep) %>%
+  summarise(total.n = n())
+
+by_group<-group_by(dat, Groep)
+mutate(distinct_groups= count(n_distinct(Groep))
+summarise(distinct_groups)
+count(dat, distinct_groups(N()))
+
+#GOT IT TO WORK:
+ddply(dat,.(Groep),
+      summarise,
+      count = length(form_nr1)
+      )
 
@@
 
+#Work on tables:
+# CODE FOR TABLE HERE:
+install.packages("tables")
+library(tables)
+install.packages("mosaic")
+library(mosaic)
+install.packages("stargazer")
+library(stargazer)
+install.packages("xtable")
+library(xtable)
+
+# using tables function, doesnt work as planned
+csvtable<-tbl_df("Experiment3_ReplicationTable_csv.csv")
+view(csvtable)
+
+tabular(dat_egood$music + 1) ~ (n+1) + Format(digits=2)* 
+          (dat_egood$chose_advertised_pen)* (n+ proportions), data=dat_egood)))
+
+#not what expected
+mosaicplot(freqtable)
+
+# better
+attach(dat_egood)
+freqtable<-table(dat_egood$music,dat_egood$chose_advertised_pen)
+freqtable
+margin.table(freqtable, 1)
+margin.table(freqtable, 2)
+prop.table(freqtable)
+proportions <-prop.table(freqtable, 1)
+proportions
+prop.table(freqtable, 2)
+
+# trying stargazer... no good
+stargazer(dat_egood[c("")], type= "text", title= "Frequencies...", digits=2, out="freqtable.txt")
+
+#
+tbl2<-tbl_df(tbl2)
+print(xtable(tbl2), type="html")
+
 ```
@@
 graph.simple = ggplot(dat, aes(x = wmc.center, y = stroop.rt)) 
-graph.simple + geom_smooth(method = "lm") +
+graph.simple + geom_smooth(method = "") +
   geom_point() +
-  ggtitle("Simple Effect of Working Memory on Stroop Performance (RT)") +
-  ylab("Stroop RT") +
-  xlab("Working Memory Deviation Score from Mean")
+  ggtitle("") +
+  ylab("") +
+  xlab("")
 
@@
   geom_point() +
-  ggtitle("Working Memory on Stroop Performance (RT)") +
-  ylab("Stroop RT") +
-  xlab("Working Memory Deviation Score from Mean")
+  ggtitle("") +
+  ylab("") +
+  xlab("")
 ```

### 2015-03-31 replication_report.Rmd
attempt to clean up

--- 2015-02-23 replication_report.Rmd
@@
 dat <- read.csv("GORN_study3.csv", header = TRUE)
-head(dat)
+dat <-tbl_df(dat)
 View(dat)
+dat %>%
+  filter(na.rm=TRUE) %>%
+  group_by(Groep) %>%
+  summarise(total.n = n())
+
+by_group<-group_by(dat, Groep)
+mutate(distinct_groups= count(n_distinct(Groep))
+summarise(distinct_groups)
+count(dat, distinct_groups(N()))
+
+#Frequencies of each group:
+ddply(dat,.(Groep),
+      summarise,
+      count = length(form_nr1)
+      )
 
@@
 
+#Work on tables:
+#In another working document (because incomplete)
 ```
@@
 ```{r, echo=FALSE}
-##Scatterplots
-graph.simple = ggplot(dat, aes(x = wmc.center, y = stroop.rt)) 
-graph.simple + geom_smooth(method = "lm") +
+##Scatterplots for add on to study graphs 
+graph.simple = ggplot(dat, aes(x = , y = )) 
+graph.simple + geom_smooth(method = "") +
   geom_point() +
-  ggtitle("Simple Effect of Working Memory on Stroop Performance (RT)") +
-  ylab("Stroop RT") +
-  xlab("Working Memory Deviation Score from Mean")
+  ggtitle("") +
+  ylab("") +
+  xlab("")
 

### 2015-04-03 replication_report.Rmd
added new table code

@@
 anova(m1.cent, m2.cent)
-
-#Work on tables:
-#In another working document (because incomplete)
 ```
 
-Graph results of moderation analysis
+```{r, echo=FALSE}
+#Work on tables:
+##Basic Table to show frequencies
+LikedMusic<- c("21(57%)","16(43%)", "")
+DislikedMusic<- c("8(23%)","27(77%)", "N= 72, χ²(1)= 8.59, p= .003,Φ=.35")
+Condition<- c("AdvertisedPen", "NonAdvertisedPen", "")
+dfFreq=cbind(Condition, LikedMusic, DislikedMusic)
 
-```{r, echo=FALSE}
+# Graph results of moderation analysis
+
 ##Scatterplots for add on to study graphs 

### 2015-04-04 working-document-notes.R
updated notes since revision to final replication .RMD

@@ -1,16 +1,16 @@
 ---
-  title: "replication report" <-- Our Working Document/ideas for extensions
+  title: "Our Working Document/ideas for extensions & notes on unused code"
 author: "Yari & Kyonne" 
-date: 
+date: "N/a"
 output: html_document
 ---
   
-  Plan for replication project
+  Plan for replication project:
 (1) Showing abbreviated version of the table 
 (2) Explain what that table displays 
 (3) R code to get there
 ----
-  Plan for added components for replication project (due later)
+  Possibilities for added components for replication project (due later)
 (1) power analyses - with and without excluded participants
 (2) moderation analysis by gender
 (3) graph the results with ggplot2
@@ -51,159 +51,57 @@ dat_e <- dat %>%
 #dat_e
 #View(dat_e)
 
-# Analyses on ENTIRE sample:
-
-# Test whether music condition is independent of pen choice:
-# (1 == liked music, 2 == disliked music)
-# (0 == not chosen, 1 == chosen)
-tbl = table(dat_e$music, dat_e$chose_advertised_pen) 
-tbl    
-
-# Chi-Square, no correction, no simulation:
-cs1 <- chisq.test(tbl, correct = FALSE)
-
-# Power analysis -- Find the power to detect .35 effect size reported in paper:
-pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)
-
-# Power analysis -- Find the effect size for a test with .8 sensitivity:
-pwr.chisq.test(w = NULL, N = 91, df = 1, sig.level = 0.05, power = .8)
-
-# Chi-Square tests - more conservative, not in the paper: 
-## With Yate's correction:
-# chisq.test(tbl)
-## No correction but a Monte Carlo simulation:
-# chisq.test(tbl, simulate.p.value = TRUE)
-
-# Analyses on SUBSETTED sample:
-
-# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:
-
-# Find Cronbach's Alpha for music attitudes scale (for comparison with article):
-# dat_music <- dat_e %>%
-# select(att_muz1, att_muz2, att_muz3) 
-# View(dat_music)
[…]

### 2015-04-26 WorkonModeration.R
separate work for moderation

@@ -1,0 +1,216 @@
+# Load packages
+library(pwr)
+library(dplyr)
+library(broom)
+library(tidyr)
+library(ggplot2)
+library(MBESS)
+library(psych)
+library(car)
+library(lsr)
+library(MASS)
+
+# Load data
+dat <- read.csv("GORN_study3.csv", header = TRUE)
+dat <- tbl_df(dat)
+#head(dat)
+#View(dat)
+
+# Designate factors:
+dat$Groep <- as.factor(dat$Groep)
+dat$music <- as.factor(dat$music)
+dat$chose_advertised_pen <- as.factor(dat$chose_advertised_pen)
+
+## Filter out 2 excluded participants who accidentily took study twice in the paper:
+dat_e <- dat %>%
+  filter(excluded == 0)
+#dat_e
+#View(dat_e)
+
+# Analyses on ENTIRE sample:
+
+# Test whether music condition is independent of pen choice:
+# (1 == liked music, 2 == disliked music)
+# (0 == not chosen, 1 == chosen)
+tbl = table(dat_e$music, dat_e$chose_advertised_pen) 
+tbl    
+
+# Chi-Square, no correction, no simulation:
+cs1 <- chisq.test(tbl, correct = FALSE)
+
+# Power analysis -- Find the power to detect .35 effect size reported in paper:
+pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)
+
+# Power analysis -- Find the effect size for a test with .8 sensitivity:
+pwr.chisq.test(w = NULL, N = 91, df = 1, sig.level = 0.05, power = .8)
+
+# Chi-Square tests - more conservative, not in the paper: 
+## With Yate's correction:
+# chisq.test(tbl)
+## No correction but a Monte Carlo simulation:
+# chisq.test(tbl, simulate.p.value = TRUE)
+
+# Analyses on SUBSETTED sample:
+
+# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:
+
+# Find Cronbach's Alpha for music attitudes scale (for comparison with article):
+# dat_music <- dat_e %>%
+# select(att_muz1, att_muz2, att_muz3) 
+# View(dat_music)
+# alpha(dat_music, na.rm = TRUE, delete=TRUE)
+
[…]

### 2015-04-26 WorkonModeration.R
deleted a couple of old unneeded things

@@ -125,27 +125,7 @@ Gender <- factor(dat_egood$geslacht1,
                     levels = c(1,2),
                     labels = c("Male", "Female"))
 
-#Test for homogeneity of variance:
-leveneTest(dat_egood$chose_advertised_pen ~ dat_egood$Male, center=mean)
-
-#simple effect of centered predictor on Y
-model.centered<-lm(dat_egood$chose_advertised_pen ~ dat_egood$Male)
-summary(model.centered)
-
-#centered models:
-m1.cent<-lm(dat_egood$chose_advertised_pen ~ dat_egood$Likedmusic.center 
-            + dat_egood$Male)
-summary(m1.cent)
-
-m2.cent<-lm(dat$Y ~ dat$X.center 
-            + dat$M
-            + (dat$X.center*dat$M))
-summary(m2.cent)
-
-#compare models
-anova(m1.cent, m2.cent)
-
-#More like a logistic regression
+#a logistic regression
 install.packages("QuantPsyc")
 library(QuantPsyc)
 

### 2015-04-26 working-document-notes.R
added glm work- add anything you would like to see

@@ -92,28 +92,74 @@ library(dplyr)
 #print(xtable(tbl2), type="html")
 
 ## Possible new contribution #1: Moderation analysis 
+#have to create dummy variables:
 
-#center predictor variable (using blanks for variable name until we get the translated documents:
-dat$X.center<-scale(dat$X, center=TRUE, scale=FALSE)
-#set moderator as a factor
-dat$M<-as.factor(dat$M)
-#Test for homogeneity of variance:
-leveneTest(dat$X ~ dat$M, center = mean)
-#simple effect of centered predictor on Y
-model.centered<-lm(dat$______ ~ dat$______.center)
-summary(model.centered)
-#centered models:
-m1.cent<-lm(dat$Y ~ dat$X.center 
-            + dat$M)
-summary(m1.cent)
+Music <- factor(dat_egood$music,
+                levels = c(1,2),
+                labels = c("LikedMusic", "DislikedMusic"))
 
-m2.cent<-lm(dat$Y ~ dat$X.center 
-            + dat$M
-            + (dat$X.center*dat$M))
-summary(m2.cent)
-#compare models
-anova(m1.cent, m2.cent)
+ChosenPen <- factor(dat_egood$chose_advertised_pen,
+                    levels = c(1,0),
+                    labels = c("ChoseAdPen", "NotChoseAdPen"))
 
+#figure out which is female and which is male in geslacht1
+count(dat_egood, geslacht1)
+
+# Gender dummy
+Gender <- factor(dat_egood$geslacht1,
+                 levels = c(1,2),
+                 labels = c("Male", "Female"))
+
+#a logistic regression
+install.packages("QuantPsyc")
+library(QuantPsyc)
+
+# for relationship between advertised pen and music, music 2 (disliked) seems significant, 
+# which is weird. 
+glm1 <- glm(ChosenPen ~ Music, data=dat_egood, family=binomial)
+summary(glm1)
+glm1prob<-predict(glm1, dat_egood, type="response")
+mean(glm1prob)
+
+# reversed previsious glm
+glm1a <- glm(Music ~ ChosenPen, data=dat_egood, family=binomial)
+summary(glm1a)
+glm1aprob<-predict(glm1a, dat_egood, type="response")
+mean(glm1aprob)
+
+# chosen pen outcome, music, and gender as moderator
[…]

### 2015-04-27 replication_report-extensions.Rmd
Extensions added to github - may have lost connection for last night's commits!

---
title: "Replication Report"
author: "Yari & Kyonne" 
date: "April 3, 2015"
output: html_document
---

(1) Replicated table:

```{r echo = FALSE}

# Load packages
suppressPackageStartupMessages(require(dplyr))
suppressPackageStartupMessages(require(tidyr))
suppressPackageStartupMessages(require(pwr)) 
suppressPackageStartupMessages(require(broom))
suppressPackageStartupMessages(require(lsr))
suppressPackageStartupMessages(require(ggplot2))
suppressPackageStartupMessages(require(MBESS))
suppressPackageStartupMessages(require(psych))
suppressPackageStartupMessages(require(car))
suppressPackageStartupMessages(require(MASS))
suppressPackageStartupMessages(require(stargazer))

Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
Disliked_Music <- c("8(23%)","27(77%)", "")
Condition <- c("AdvertisedPen", "NonAdvertisedPen", "Chi-Square")
Freq_Table = cbind(Condition, Liked_Music, Disliked_Music)
stargazer(Freq_Table, type = "text", title = "Study 3: Frequencies of Pen Choice for Each Conditon & Chi-Square")

```

(2) Explanation: 
The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions, respectively, in Study 3. Note that at the bottom of the table is also the chi-square statistic, p-value and effect size (phi) for the data, indicating a medium-sized effect of music condition on pen choice. The table also demonstrates that the frequency of choice in the Disliked Music condition was in the hypothesized direction: Subjects tended to choose the non-advertised pen when made to listen to disliked music in an advertisement. Please note that the data represented above follows the exclusion criteria set forth in the published article. Specifically, any subjects who had participated in a prior version of the study were excluded (two subjects). In addition, 19 subjects were excluded for their so-called "deviant music evaluations". These subjects were foundd to either somewhat dislike the "liked music" (music attiude score below 3) or somewhat like the "disliked music" (music attitude score above 3).

(3) Code for analyses & table:

```{r eval= FALSE}

# Load data
dat <- read.csv("GORN_study3.csv", header = TRUE)
dat <- tbl_df(dat)
#head(dat)
#View(dat)

# Designate factors:
dat$Groep <- as.factor(dat$Groep)
dat$music <- as.factor(dat$music)
dat$chose_advertised_pen <- as.factor(dat$chose_advertised_pen)

# Filter out 2 excluded participants who accidentily took study twice in the paper:
dat_e <- dat %>%
  filter(excluded == 0)
#dat_e
#View(dat_e)

## Analyses on ENTIRE sample:

# Test whether music condition is independent of pen choice:
# (1 == liked music, 2 == disliked music)
# (0 == not chosen, 1 == chosen)
tbl <- table(dat_e$music, dat_e$chose_advertised_pen) 
tbl

# Chi-Square, no correction, no simulation:
cs1 <- chisq.test(tbl, correct = FALSE)

# Power analysis -- Find the power to detect .35 effect size reported in paper:
pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)

# Power analysis -- Find the effect size for a test with .8 sensitivity:
pwr.chisq.test(w = NULL, N = 91, df = 1, sig.level = 0.05, power = .8)

# Analyses on SUBSETTED sample:

# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:

# Find Cronbach's Alpha for music attitudes scale (for comparison with article):
#dat_music <- dat_e %>%
#  select(att_muz1, att_muz2, att_muz3)
#View(dat_music)
#alpha(dat_music, na.rm = TRUE, delete=TRUE)

# Find mean attitudes for each music condition (for comparison with article): 
#dat_e %>%
#  group_by(music) %>%
#  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))

# Add mean attitude column to dataframe:
dat_e <- dat_e %>%
  mutate(avg_att_muz = (att_muz1 + att_muz2 + att_muz3) / 3)
#View(dat_e)

# Check those means (for comparison with article):
#dat_e %>%
#  group_by(music) %>%
#  summarise(avg = mean(avg_att_muz))

# Exclude when average attitude > 3 in disliked cond. or average attitude <3 for liked cond. (1 == liked music, 2 == disliked music)
dat_egood <- dat_e %>%
  filter(music == 1 & avg_att_muz > 3 | music == 2 & avg_att_muz < 3)
#View(dat_egood)

## Redo Chi-Square with subsetted data:

# Test whether music condition is independent of pen choice:
# Create 2x2 contingency table of frequencies - pen choice by music condition
tbl2 <- table(dat_egood$music, dat_egood$chose_advertised_pen) 
tbl2

# Chi-Square, no correction, no simulation:
cs2 <- chisq.test(tbl2, correct = FALSE)
tidy(cs2)

# Power analysis -- Find the power to detect .35 effect size reported in paper:
pwr.chisq.test(w = .35, N = 72, df = 1, sig.level = 0.05, power = NULL)

# Power analysis -- Find the effect size for a test with minimum of .8 sensitivity:
pwr.chisq.test(w = NULL, N = 72, df = 1, sig.level = 0.05, power = .8)

# Confidence Intervals (not replicated from paper):
#upper (95%)
#CI95_up <- qchisq(.95, df = 1)
#lower (5%)
#CI95_low <- qchisq(.05, df = 1)

## Replicate Table: Frequency table & chi-square statistic of subsetted data
# (replicate "Experiment 3" portion of the table from article)

# Generate count and proportion (percent) tallies for replicating the table:
# Amongst those in Liked Music condition:
dat_egoodLike <- dat_egood %>%
  filter(music == 1)
dat_egoodLike %>%
  group_by(chose_advertised_pen) %>%
  summarise(n = n(),
            percent = n / nrow(dat_egoodLike) * 100)

# Amongst those in Disliked Music condition:
dat_egoodDislike <- dat_egood %>%
  filter(music == 2)
dat_egoodDislike %>%
  group_by(chose_advertised_pen) %>%
  summarise(n = n(),
            percent = n / nrow(dat_egoodDislike) * 100)

# Generate table:
Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
Disliked_Music <- c("8(23%)","27(77%)", "")
Condition <- c("AdvertisedPen", "NonAdvertisedPen", "Chi-Square")
Freq_Table <- cbind(Condition, Liked_Music, Disliked_Music)
stargazer(Freq_Table, type = "text", title = "Study 3: Frequencies of Pen Choice for Each Conditon & Chi-Square")

```

(4.1) Extension A: Graphing the frequency of response & Investigating moderation by gender:

```{r echo = FALSE}

ggplot(dat_egood, 
       aes(x = music, fill = chose_advertised_pen)) +
  geom_bar(stat = "bin",
           position = position_dodge()) + 
  scale_fill_brewer(name = "Pen Choice", 
                    labels = c("Not Advertised", "Advertised"), palette = "Set2") +
  ggtitle("Frequency of Pen Choice By Condition") +
  ylab("Frequency") +
  xlab("Music Conditon") +
  scale_x_discrete(breaks=c("1", "2"), 
                   labels=c("Liked", "Disliked")) +
  theme_bw() + 
  theme(axis.title.x = element_text(face = 'bold', size = 15),
        axis.title.y = element_text(face = 'bold', size = 15), 
        plot.title = element_text(face = 'bold', size = 20),
        legend.title = element_text(face = 'bold', size = 12),
        legend.text = element_text(size = 12),
        axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12))
```

(4.1.1) Code for graph and moderation analyses:

```{r eval = FALSE}

# Graph the number of participants who chose each pen, by music condition:
ggplot(dat_egood, 
       aes(x = music, fill = chose_advertised_pen)) +
  geom_bar(stat = "bin",
           position = position_dodge()) + 
  scale_fill_brewer(name = "Pen Choice", 
                    labels = c("Not Advertised", "Advertised"), palette = "Set2") +
  ggtitle("Frequency of Pen Choice By Condition") +
  ylab("Frequency") +
  xlab("Music Conditon") +
  scale_x_discrete(breaks=c("1", "2"), 
                   labels=c("Liked", "Disliked")) +
  theme_bw() + 
  theme(axis.title.x = element_text(face = 'bold', size = 15),
        axis.title.y = element_text(face = 'bold', size = 15), 
        plot.title = element_text(face = 'bold', size = 20),
        legend.title = element_text(face = 'bold', size = 12),
        legend.text = element_text(size = 12),
        axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12))

```

(4.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.

Since the musical stimulus chosen for manipulation in this study was performed by a female artist, it is possible that the strength of aversion to the advertised pen (when paired with a disliked music) would be different by gender. Note: We are quite underpowered to conduct this test as a confirmatory analysis, and there is little theoretical precedent for looking at gender differences in pen choice; thus, this was an entirely exploratory investigation. It is possible that the disliked (and distorted sound) of the female singer's voice impacted women more so than men, such that women had an even greater liklihood of choosing the non-advertised pen when assigned to the disliked-music conditioin. However, as displayed in our analyses of the predicted probabilities below, first for the entire sample, and then for the data subsetted by gender, the likelihood of men and women chosing the advertised or non-advertised pen in each condition is nearly identitical. A greater sampling of men (as well as women) would be needed in order to test this hypothesis with greater statistical power.

(4.2.1) A quick check of N by gender in data:

```{r echo = FALSE}

#Get counts and check values against article for correct coding scheme:
count(dat_egood, geslacht1)
#confirmed:
## 1 = male
## 2 = female

```

(4.2.2) Code for logistical regressions:

```{r eval = FALSE}

#Recode dummy variable for music as 0 and 1 for easier interpretation of estimates:
Music <- factor(dat_egood$music,
                    levels = c(1,2),
                    labels = c("LikedMusic", "DislikedMusic"))

dat_egood$music <- as.numeric(dat_egood$music)
dat_egood <- dat_egood %>%
  mutate(music.recode2 = (music - 1))
View(dat_egood)

#Set factor names:
Music <- factor(dat_egood$music.recode2,
                    levels = c(0, 1),
                    labels = c("Liked", "DisLiked"))

ChosenPen <- factor(dat_egood$chose_advertised_pen,
                levels = c(1, 0),
                labels = c("ChoseAdPen", "NotChoseAdPen"))

#Compare counts of each gender in paper to data for coding:
count(dat_egood, geslacht1)
## 1 = male
## 2 = female

# need to check which is which:
Gender <- factor(dat_egood$geslacht1,
                    levels = c(1,2),
                    labels = c("Male", "Female"))

# for relationship between advertised pen and music, music 2 (disliked) seems significant:
fit1 <- glm(ChosenPen ~ Music, data = dat_egood, family = binomial)
fit1 <- tidy(fit1)
fit1

#### calculate odds 
fit1$estimate
fit1$estimate[1] + fit1$estimate[2] ## 1.216
## odds ratio
exp(fit1$estimate[2]) ##4.43
## predicted probabilities:
# Disliked Music:
(exp(fit1$estimate[1] + fit1$estimate[2])) / (1 + exp(fit1$estimate[1] + fit1$estimate[2]))
# Liked Music: 
exp(fit1$estimate[1]) / (1 + exp(fit1$estimate[1]))

# does the relationship change when looking ONLY at males & ONLY females?

male.dat_egood <- dat_egood %>%
  filter(geslacht1 == "1")
#count(male.dat_egood, geslacht1)

female.dat_egood <- dat_egood %>%
  filter(geslacht1 == "2")
#count(female.dat_egood, geslacht1)

# MALES:
fitmale <- glm(ChosenPen ~ Music, data = male.dat_egood, family=binomial)
fitmale <- tidy(fitmale)
fitmale
#### calculate odds 
fitmale$estimate
fitmale$estimate[1] + fitmale$estimate[2] ## 1.216
## odds ratio
exp(fitmale$estimate[2]) ##4.43

# FEMALES:
fitfemale <- glm(ChosenPen ~ Music, data = female.dat_egood, family=binomial)
fitfemale <- tidy(fitfemale)
fitfemale
#### calculate odds 
fitfemale$estimate
fitfemale$estimate[1] + fitfemale$estimate[2] ## 1.216
## odds ratio
exp(fitfemale$estimate[2]) ## 4.43

### predicted probabilities = confirmed, gender does not have a moderating effect on the likelihood 
# of choosing the advertised pen when listening to liked versus disliked music.
# Males - Disliked Music = 0.77
(exp(fitmale$estimate[1] + fitmale$estimate[2])) / 
  (1 + exp(fitmale$estimate[1] + fitmale$estimate[2])) 
# Males - Liked Music = 0.43
exp(fitmale$estimate[1]) / (1 + exp(fitmale$estimate[1]))

# Females - Disliked Music = 0.77
(exp(fitfemale$estimate[1] + fitfemale$estimate[2])) / 
  (1 + exp(fitfemale$estimate[1] + fitfemale$estimate[2])) 
# Males - Liked Music = 0.43
exp(fitfemale$estimate[1]) / (1 + exp(fitfemale$estimate[1]))

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the table. Further, the "eval = FALSE" parameter was added to the top code chunk to prevent printing of the code.

### 2015-04-27 WorkonModeration.R

@@ -107,82 +107,105 @@ pwr.chisq.test(w = NULL, N = 72, df = 1, sig.level = 0.05, power = .8)
 ## No correction but a Monte Carlo simulation:
 # chisq.test(tbl2, simulate.p.value = TRUE)
 
-#have to create dummy variables:
+# Logistic Regressions
+library(ggplot2)
+library(tidyr)
+library(dplyr)
+library(stargazer)
 
+
+#Create dummy variables:
 Music <- factor(dat_egood$music,
                     levels = c(1,2),
                     labels = c("LikedMusic", "DislikedMusic"))
+
+
+#Recode dummy variables:
+dat_egood$music <- as.numeric(dat_egood$music)
+dat_egood <- dat_egood %>%
+  mutate(music.recode2 = (music - 1))
+View(dat_egood)
+
+#Set factors:
+Music <- factor(dat_egood$music.recode2,
+                    levels = c(0, 1),
+                    labels = c("Liked", "DisLiked"))
 
 ChosenPen <- factor(dat_egood$chose_advertised_pen,
                 levels = c(1,0),
                 labels = c("ChoseAdPen", "NotChoseAdPen"))
 
-#figure out which is female and which is male in geslacht1
+#Compare counts of each gender in paper to data for coding:
 count(dat_egood, geslacht1)
+## 1 = male
+## 2 = female
 
 # need to check which is which:
 Gender <- factor(dat_egood$geslacht1,
                     levels = c(1,2),
                     labels = c("Male", "Female"))
 
-#a logistic regression
-install.packages("QuantPsyc")
-library(QuantPsyc)
+# for relationship between advertised pen and music, music 2 (disliked) seems significant:
+fit1 <- glm(ChosenPen ~ Music, data = dat_egood, family = binomial)
+fit1 <- tidy(fit1)
+fit1
 
-# for relationship between advertised pen and music, music 2 (disliked) seems significant, 
-# which is weird. 
-glm1 <- glm(ChosenPen ~ Music, data=dat_egood, family=binomial)
-summary(glm1)
-glm1prob<-predict(glm1, dat_egood, type="response")
-mean(glm1prob)
+#### calculate odds 
+fit1$estimate
[…]

### 2015-05-11 replication_report-extensions.Rmd
date change.
start of final version of replication project

@@
 ---
-title: "Replication Report"
+title: "Soc504 Replication Project Report"
 author: "Yari & Kyonne" 
-date: "April 3, 2015"
+date: "May 10, 2015"
 output: html_document
@@
 
-(1) Replicated table:
+TABLE OF CONTENTS:
+1 - Synopsis of report.
+2 - Replication of original results.
+  2.1 - Image of replicated table.
+  2.2 - Explanation/description of table results.
+  2.3 - Code for replicated table, chi-square analyses and power analyses.
+3 - Extensions.
+  3.1 - Extension (A): Frequency graph.
+    3.1.1 - Code for graph.
+  3.2 - Extension (B): Moderation analysis by gender.
+    3.2.1 - Check of cell sizes for each gender.
+    3.2.2 - Code for logistic regression for moderation analysis.
+
+(1) Synopsis.
+This report encompasses the work done to first replicate, and then extend, the findings of Study 3 from Vermeulen et al.
+(2014).
+The authors of the original article wanted to know whether single exposure to a certain kind of music (music that is either widely liked or disliked) will condition participants to choose one pen over another.
+Specifically, they hypothesize that participants exposed to liked music will be conditioned to choose the pen that was advertised while the music is playing; and likewise, participants exposed to disliked music will be conditioned to choose an alternative pen to the one advertised while the music is playing.
+
+Section (2) details our replication process. We reproduce the single figure from the article, a frequency table for the outcome of interest in Study 3 as well as all the chi-square analyses.
+
+Section (3) comprises our two-part extension process.
+First, we create a bar graph of the frequencies detailed in the original article's table.
+Second, we statistically test for any moderation of our results by gender, using subsetting the data by gender and then conducting separate logistic regression analyses.
+From there, we looked for any differences between men and women in the predicted probability of the key outcome variable (pen choice).
+
+(2.1) Replicated table.
+Note: the `echo = FALSE` parameter was added to the below code chunk to prevent printing of the R code that generated the table. See section (2.3) for the full code.
 
@@
 
-# Load packages
+# Load packages:
 suppressPackageStartupMessages(require(dplyr))
@@
 
+# Derrive table of frequencies:
 Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
@@
 
-(2) Explanation: 
+(2.2) Explanation.
 The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions, respectively, in Study 3.
@@
 
-(3) Code for analyses & table:
+(2.3) Code for analyses & table.
+Note: the 'eval = FALSE' parameter was added to this code chunk to prevent printing of the code.
 
@@
 dat <- tbl_df(dat)
-#head(dat)
-#View(dat)
 
@@
   filter(excluded == 0)
-#dat_e
-#View(dat_e)
 
@@
 # Test whether music condition is independent of pen choice:
-# (1 == liked music, 2 == disliked music)
-# (0 == not chosen, 1 == chosen)
+# "music"" variable: (1 == liked music, 2 == disliked music)
+# "chose_advertised_pen" variable: (0 == not chosen, 1 == chosen)
 tbl <- table(dat_e$music, dat_e$chose_advertised_pen)
-tbl
 
@@
 
-# Power analysis -- Find the power to detect .35 effect size reported in paper:
+# Power analysis -- Find the power to detect the .35 effect size reported in paper:
 pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)
@@
 
-# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:
+# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition (reported ratings above 3) & too negative attitudes in "liked music" condition (reported ratings below 3):
 
 # Find Cronbach's Alpha for music attitudes scale (for comparison with article):
-#dat_music <- dat_e %>%
-#  select(att_muz1, att_muz2, att_muz3)
-#View(dat_music)
-#alpha(dat_music, na.rm = TRUE, delete=TRUE)
+dat_music <- dat_e %>%
+  select(att_muz1, att_muz2, att_muz3)
+
+alpha(dat_music, na.rm = TRUE, delete=TRUE)
 
 # Find mean attitudes for each music condition (for comparison with article): 
-#dat_e %>%
-#  group_by(music) %>%
-#  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))
+dat_e %>%
+  group_by(music) %>%
+  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))
 
@@
   mutate(avg_att_muz = (att_muz1 + att_muz2 + att_muz3) / 3)
-#View(dat_e)
 
 # Check those means (for comparison with article):
-#dat_e %>%
-#  group_by(music) %>%
-#  summarise(avg = mean(avg_att_muz))
+dat_e %>%
+  group_by(music) %>%
+  summarise(avg = mean(avg_att_muz))
 
-# Exclude when average attitude > 3 in disliked cond. or average attitude <3 for liked cond. (1 == liked music, 2 == disliked music)
+# Exclude when average attitude > 3 in disliked cond. or average attitude < 3 for liked cond. (1 == liked music, 2 == disliked music)
 dat_egood <- dat_e %>%
   filter(music == 1 & avg_att_muz > 3 | music == 2 & avg_att_muz < 3)
-#View(dat_egood)
 
@@
 
-(4.1) Extension A: Graphing the frequency of response & Investigating moderation by gender:
+(3.1) Extension A: Graphing the frequency of responses in each condition.
 
@@
 
-(4.1.1) Code for graph and moderation analyses:
+(3.1.1) Code for graph.
 
@@
 
-(4.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.
+(3.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.
 
@@
 
-(4.2.1) A quick check of N by gender in data:
+(3.2.1) A quick check of N by gender in data.
 
@@
 
-(4.2.2) Code for logistical regressions:
+(3.2.2) Code for logistical regressions.
 
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the table.
-Further, the "eval = FALSE" parameter was added to the top code chunk to prevent printing of the code.
+Further, the 'eval = FALSE' parameter was added to the top code chunk to prevent printing of the code.

### 2015-05-11 replication_report-extensions.Rmd
second draft of final version of report

@@
 
-TABLE OF CONTENTS:
-1 - Synopsis of report.
-2 - Replication of original results.
-  2.1 - Image of replicated table.
+## TABLE OF CONTENTS:
+Section | Contents
+--------|---------
+1       | Synopsis.
+2       | Replication of original results & figures.
+3       | Extensions.
+
+**1 - Synopsis of report.**
+**2 - Replication of original results.**
+  2.1 - Table of frequencies.
+    2.1.1 - Original table (copy/pasted & abbreviated to only show Study 3 results).
+    2.1.2 - Replicated table using R code.
   2.2 - Explanation/description of table results.
   2.3 - Code for replicated table, chi-square analyses and power analyses.
-3 - Extensions.
+**3 - Extensions.**
   3.1 - Extension (A): Frequency graph.
@@
 
-(1) Synopsis.
+### (1) Synopsis.
 This report encompasses the work done to first replicate, and then extend, the findings of Study 3 from Vermeulen et al.
@@
 
-(2.1) Replicated table.
+### (2.1.1) Original table.
+![Abbreviated figure from the original article.](original-figure-S3.png)
+
+### (2.1.2) Replicated table.
 Note: the `echo = FALSE` parameter was added to the below code chunk to prevent printing of the R code that generated the table. See section (2.3) for the full code.
 
-```{r echo = FALSE}
+```{r echo = FALSE, warning = FALSE}
 
@@
 
-(2.2) Explanation.
+### (2.2) Explanation.
 The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions, respectively, in Study 3.
@@
 
-(2.3) Code for analyses & table.
-Note: the 'eval = FALSE' parameter was added to this code chunk to prevent printing of the code.
+### (2.3) Code for analyses & table.
+Note: the 'eval = FALSE' parameter was added to this code chunk to prevent printing of command outputs superfluous to the results reported in the original paper.
 
@@
 ## Redo Chi-Square with subsetted data:
-
 # Test whether music condition is independent of pen choice:
@@
 
-(3.1) Extension A: Graphing the frequency of responses in each condition.
+### (3.1) Extension A: Graphing the frequency of responses in each condition.
 
@@
 
-(3.1.1) Code for graph.
+#### (3.1.1) Code for graph.
 
@@
 
-(3.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.
+### (3.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.
 
@@
 
-(3.2.1) A quick check of N by gender in data.
+#### (3.2.1) A quick check of N by gender in data.
 
@@
 
-(3.2.2) Code for logistical regressions.
+#### (3.2.2) Code for logistical regressions.
 
@@
 ```
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the table.
-Further, the 'eval = FALSE' parameter was added to the top code chunk to prevent printing of the code.
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the figures.
+Further, the 'eval = FALSE' parameter was added to the top code chunk to prevent printing of the code along with any generated figures

### 2015-05-12 replication_report-extensions.Rmd
final version of replication report

@@
 author: "Yari & Kyonne" 
-date: "May 10, 2015"
+date: "May 12, 2015"
 output: html_document
@@
 
-```{r eval= FALSE}
+```{r}
 
@@
 cs1 <- chisq.test(tbl, correct = FALSE)
+cs1 <- tidy(cs1)
 
@@
 pwr.chisq.test(w = NULL, N = 91, df = 1, sig.level = 0.05, power = .8)
+```
 
-# Analyses on SUBSETTED sample:
+Chi-square analyses on the entire sample replicate the results reported in the article and confirm that participants in the liked and disliked music condition did not choose the advertised pen at an equal rate (chi-square = *`r cs1[1,1]`*, *p = `r cs1[1,2]`*).
 
-# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition (reported ratings above 3) & too negative attitudes in "liked music" condition (reported ratings below 3):
+```{r, eval=FALSE}
+
+## Analyses on SUBSETTED sample:
+
+# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition (reported ratings above 3 in attitudes survey) & too negative attitudes in "liked music" condition (reported ratings below 3):
 
@@
 
+# Check the grand/group-level means (for comparison with article):
+dat_e %>%
+  group_by(music) %>%
+  summarise(avg = mean(avg_att_muz))
+
+```
+
+```{r}
+
+# Exclude participants with average attitude > 3 in disliked condition or average attitude < 3 for liked condition (1 == liked music, 2 == disliked music)
+
 # Add mean attitude column to dataframe:
@@
 
-# Check those means (for comparison with article):
-dat_e %>%
-  group_by(music) %>%
-  summarise(avg = mean(avg_att_muz))
-
-# Exclude when average attitude > 3 in disliked cond. or average attitude < 3 for liked cond. (1 == liked music, 2 == disliked music)
+# Create a new dataframe "dat_egood" with filtered participants:
 dat_egood <- dat_e %>%
@@
 tbl2 <- table(dat_egood$music, dat_egood$chose_advertised_pen)
-tbl2
 
@@
 cs2 <- chisq.test(tbl2, correct = FALSE)
-tidy(cs2)
+cs2 <- tidy(cs2)
 
@@
 
-# Confidence Intervals (not replicated from paper):
+# Confidence Intervals (these were not reported in paper, just for curiosity):
 #upper (95%)
@@
 
+```
+
+Chi-square analyses on the subsetted sample replicate from the paper and further confirm that participants in the liked and disliked music condition did not choose the advertised pen at an equal rate (chi-square = *`r cs2[1,1]`*, *p = `r cs2[1,2]`*).
+
+```{r, eval=FALSE}
+
 ## Replicate Table: Frequency table & chi-square statistic of subsetted data
+
 # (replicate "Experiment 3" portion of the table from article)
@@
 ### (3.1) Extension A: Graphing the frequency of responses in each condition.
+Note: the parameter "echo = FALSE" was added to this code chunk to prevent the printing of the code. For the code related to this graph, see section (3.1.1).
 
@@
 #### (3.1.1) Code for graph.
+Note: the "eval = FALSE" parameter was added to prevent the rendering of the figure. To observe the figure, see section (3.1).
 
@@
 
-#### (3.2.1) A quick check of N by gender in data.
+#### (3.2.1) A quick check of N by gender in data show a heavy proportion of females were sampled.
 
@@
 count(dat_egood, geslacht1)
-#confirmed:
+#confirmed coding scheme:
 ## 1 = male
@@
 
-#### (3.2.2) Code for logistical regressions.
+#### (3.2.2) Code and analysis results for logistical regressions.
 
-```{r eval = FALSE}
+```{r}
 
-#Recode dummy variable for music as 0 and 1 for easier interpretation of estimates:
-Music <- factor(dat_egood$music,
-                    levels = c(1,2),
-                    labels = c("LikedMusic", "DislikedMusic"))
-
+# Recode dummy variable for music as 0 and 1 for easier interpretation of estimates:
 dat_egood$music <- as.numeric(dat_egood$music)
@@
   mutate(music.recode2 = (music - 1))
-View(dat_egood)
 
 #Set factor names:
-Music <- factor(dat_egood$music.recode2,
+music_condition <- factor(dat_egood$music.recode2,
                     levels = c(0, 1),
@@
 
-ChosenPen <- factor(dat_egood$chose_advertised_pen,
+pen_choice <- factor(dat_egood$chose_advertised_pen,
                 levels = c(1, 0),
@@
 
-#Compare counts of each gender in paper to data for coding:
-count(dat_egood, geslacht1)
-## 1 = male
-## 2 = female
-
-# need to check which is which:
-Gender <- factor(dat_egood$geslacht1,
+gender <- factor(dat_egood$geslacht1,
                     levels = c(1,2),
@@
 
-# for relationship between advertised pen and music, music 2 (disliked) seems significant:
-fit1 <- glm(ChosenPen ~ Music, data = dat_egood, family = binomial)
+# for relationship between advertised pen and music:
+fit1 <- glm(pen_choice ~ music_condition, data = dat_egood, family = binomial)
 fit1 <- tidy(fit1)
@@
 #### calculate odds 
-fit1$estimate
-fit1$estimate[1] + fit1$estimate[2] ## 1.216
+fit1$estimate[1] + fit1$estimate[2]
+
 ## odds ratio
-exp(fit1$estimate[2]) ##4.43
+exp(fit1$estimate[2])
+
 ## predicted probabilities:
@@
 
-# does the relationship change when looking ONLY at males & ONLY females?
+# Does the relationship change when looking ONLY at males & ONLY females?
 
@@
   filter(geslacht1 == "1")
+##double-check correct filtering:
 #count(male.dat_egood, geslacht1)
@@
   filter(geslacht1 == "2")
+##double-check correct filtering:
 #count(female.dat_egood, geslacht1)
@@
 # MALES:
-fitmale <- glm(ChosenPen ~ Music, data = male.dat_egood, family=binomial)
+fitmale <- glm(pen_choice ~ music_condition, data = male.dat_egood, family=binomial)
 fitmale <- tidy(fitmale)
 fitmale
+
 #### calculate odds 
-fitmale$estimate
-fitmale$estimate[1] + fitmale$estimate[2] ## 1.216
+fitmale$estimate[1] + fitmale$estimate[2]
 ## odds ratio
-exp(fitmale$estimate[2]) ##4.43
+exp(fitmale$estimate[2])
 
 # FEMALES:
-fitfemale <- glm(ChosenPen ~ Music, data = female.dat_egood, family=binomial)
+fitfemale <- glm(pen_choice ~ music_condition, data = female.dat_egood, family=binomial)
 fitfemale <- tidy(fitfemale)
 fitfemale
+
 #### calculate odds 
-fitfemale$estimate
-fitfemale$estimate[1] + fitfemale$estimate[2] ## 1.216
+fitfemale$estimate[1] + fitfemale$estimate[2]
 ## odds ratio
-exp(fitfemale$estimate[2]) ## 4.43
+exp(fitfemale$estimate[2])
 
@@
 # of choosing the advertised pen when listening to liked versus disliked music.
-# Males - Disliked Music = 0.77
+# Males - Disliked Music
 (exp(fitmale$estimate[1] + fitmale$estimate[2])) / 
   (1 + exp(fitmale$estimate[1] + fitmale$estimate[2])) 
-# Males - Liked Music = 0.43
+# Males - Liked Music
 exp(fitmale$estimate[1]) / (1 + exp(fitmale$estimate[1]))
 
-# Females - Disliked Music = 0.77
+# Females - Disliked Music
 (exp(fitfemale$estimate[1] + fitfemale$estimate[2])) / 
   (1 + exp(fitfemale$estimate[1] + fitfemale$estimate[2])) 
-# Males - Liked Music = 0.43
+# Females - Liked Music
 exp(fitfemale$estimate[1]) / (1 + exp(fitfemale$estimate[1]))
@@
 ```
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the figures.
-Further, the 'eval = FALSE' parameter was added to the top code chunk to prevent printing of the code along with any generated figures
+The predicted probabilities for participants' pen choice in either the liked or disliked conditions did not change after splitting the sample by gender.
+Males and females were equally likely to choose the same pen, regardless of their assigned condition.
+However, these results should be qualified by the observation that this data contained over triple the number of female participants as male participants.

### 2015-05-12 response_to_reviewers.Rmd
Revisions to Report & Review Response documents in order to address formatting issues and minor inconsistencies

---
title: "response_to_reviewers"
author: "Yari & Kyonne"
date: "Tuesday, May 12, 2015"
output: html_document
---

To whom this concerns,

We'd like to thank our reviewers for their generous comments and sage suggestions for how we can improve our write up of the replication report.

In an effort to better orient the reader to our current context, and details such as the research question from the original article, our approach to the project, and what to expect for our results, we've added a table of contents and synopsis at the top of the document.

Additionally, some reviewers had questions as to why certain parameters were added to code chunks (e.g., "echo=FALSE", which hides the code from the HTML knitted file); and so, we've added notes under the headings for each section to explain where readers can expect to find corresponding code when it is masked to produce a figure. The code for our graph includes many indentations in order to facilitate the reading of our commands in ggplot2. We have also reviewed this code to ensure that the identation remains consistent throughout. Nevertheless, we acknowledge that this approach to code writing in ggplot2 is a matter of taste.

We'd like to further thank reviewers for pointing out the places wherein the comments in our code included the output statistics. We've taken better advantage of the dynamic functionality of R Markdown documents and embedded those statistical outputs into our text explanations. This will allow for any future knitted files still reflect the most-current statistics, should the underlying dataframe be amended. We've also removed some code chunk parameters so that our knitted HTML file displayed both the code, odds ratios and predicted probabilities from our logistic regression analyses.

We have also taken time to remove any "View()" functions (whether or not they were included as a comment), since this function can interfere with furture knitting of the RMD file. Many of our variable names have also been amended to feature a consistent coding style throughout the document (e.g., all variable names are no longer capitalised). This will also help the reader better distinguish between when we are assigning/recoding variables and when we are configuring them as labels for our figures in the code.

Although we acknowledge that some variable names are not entirely descriptive, we've kept many of the names in order to be conscise in our coding style. However, where necessary, we have included more descriptive comments to better help guide our readers. Along those same lines, in our comments we've attempted to better describe the places in our code where we are merely checking our assumptions ahead of statistical analyses and where we are performing tests to directly compare our output to that from the original article. Also, some of the variable naming, particularly within functions, e.g.: "pwr.chisq.test()", was specific to the command structure of our analyses; and so we could not change them. However, we do strongly encourage the use of the R-helper shortcuts (i.e., "??[function here]") for further review of the command structures for functions, should our readers have questions about what certain abbreviations stand to represent.

As one reviewer pointed out, some code for the logistic regression was superfulous/redundant to analyses. We have deleted the redundancies while also preserving the integrity of the analyses.

Also, we were asked by a reviewer to consider plotting the results of our logistic regression by gender at the bottom of our report. While we enthusiastically believe in the importance of visualizations, we also recognize the recommendations of many other researchers regarding the consequence of plotting a categorical predictor (condition) against a binary outcome (pen choice) without any mixed-effects: compared to graphs with continuous predictors, a graph of our analyses would contribute much less to readers' understanding of the null finding. As a result, we've amended the parameters of our RMD file in order to ensure that the predicted probabilties for each gender print out clearly for the reader to see and compare directly. Furthermore, we have included summarizing paragraphs for all our statistical analyses. These paragraphs follow the code chunks representing our efforts for each analysis.

And finally, upon the recommendation of several reviewers, we've added an image of the original figure, a table of frequencies, that we sought to reproduce in this project. Please note that this table is an abbreviated version, amended only slightly from the published version to relfect only the information pertinent to the study we replicate (the original contains results from studies for which we lacked data).

Thanks again to all the eyes we've had on our report. We sincerely believe that all the feedback, encouragement and recommendations have resulted in the strongest version of our report possible. And for that, we are grateful!

Regards,

Yaritza Perez-Hooks & Kyonne Isaac

### 2015-05-12 replication_report-extensions.Rmd
Revisions to Report & Review Response documents in order to address formatting issues and minor inconsistencies

@@
 
-## TABLE OF CONTENTS:
+### TABLE OF CONTENTS:
 Section | Contents
@@
 ggplot(dat_egood, 
-       aes(x = music, fill = chose_advertised_pen)) +
+       aes(x = music, 
+           fill = chose_advertised_pen)) +
   geom_bar(stat = "bin",
@@
   scale_fill_brewer(name = "Pen Choice", 
-                    labels = c("Not Advertised", "Advertised"), palette = "Set2") +
+                    labels = c("Not Advertised", "Advertised"), 
+                    palette = "Set2") +
   ggtitle("Frequency of Pen Choice By Condition") +
@@
   xlab("Music Conditon") +
-  scale_x_discrete(breaks=c("1", "2"), 
-                   labels=c("Liked", "Disliked")) +
+  scale_x_discrete(breaks = c("1", "2"), 
+                   labels = c("Liked", "Disliked")) +
   theme_bw() + 
@@
 ```{r}
+# code for the logistic regressions was copy-pasted, then customized to fit the current data, from scripts produced during the class lab sessions (author: Angela R. Dixon)
 
@@
 Males and females were equally likely to choose the same pen, regardless of their assigned condition.
-However, these results should be qualified by the observation that this data contained over triple the number of female participants as male participants.
+However, these results should be qualified by the observation that this data contained over triple the number of female participants as male participants (see section 3.2.1).

### 2015-05-13 replication_report.Rmd

--- 2015-03-31 replication_report.Rmd
@@
 ---
-title: "replication_report"
+title: "Replication Report"
 author: "Yari & Kyonne" 
-date: "February 22, 2015"
+date: "April 3, 2015"
 output: html_document
@@
 
-Plan for replication project
-(1) power analyses - with and without outliers
-(2) moderation analysis by gender
-(3) graph the results with ggplot2
+(1) Replicated table:
 
-1: Get data
-```{r}
-#load packages:
-library(pwr)
-library(dplyr)
-library(plyr)
-library(ggplot2)
-library(MBESS)
-library(psych)
-library(car)
-library(lsr)
+```{r echo = FALSE}
 
-#load data:
-dat <- read.csv("GORN_study3.csv", header = TRUE)
-dat <-tbl_df(dat)
-View(dat)
-dat %>%
-  filter(na.rm=TRUE) %>%
-  group_by(Groep) %>%
-  summarise(total.n = n())
+# Load packages
+suppressPackageStartupMessages(require(dplyr))
+suppressPackageStartupMessages(require(tidyr))
+suppressPackageStartupMessages(require(pwr)) 
+suppressPackageStartupMessages(require(broom))
+suppressPackageStartupMessages(require(lsr))
+suppressPackageStartupMessages(require(ggplot2))
+suppressPackageStartupMessages(require(MBESS))
+suppressPackageStartupMessages(require(psych))
+suppressPackageStartupMessages(require(car))
+suppressPackageStartupMessages(require(MASS))
+suppressPackageStartupMessages(require(stargazer))
 
-by_group<-group_by(dat, Groep)
-mutate(distinct_groups= count(n_distinct(Groep))
-summarise(distinct_groups)
-count(dat, distinct_groups(N()))
+Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
+Disliked_Music <- c("8(23%)","27(77%)", "")
+Condition <- c("AdvertisedPen", "NonAdvertisedPen", "Chi-Square")
+Freq_Table = cbind(Condition, Liked_Music, Disliked_Music)
+stargazer(Freq_Table, type = "text", title = "Study 3: Frequencies of Pen Choice for Each Conditon & Chi-Square")
 
-#Frequencies of each group:
-ddply(dat,.(Groep),
-      summarise,
-      count = length(form_nr1)
-      )
-
-#center predictor variable (using blanks for variable name until we get the translated documents:
-dat$X.center<-scale(dat$X, center=TRUE, scale=FALSE)
-
-#set moderator as a factor
-dat$M<-as.factor(dat$M)
-
-#Test for homogeneity of variance:
-leveneTest(dat$X ~ dat$M, center = mean)
-
-#simple effect of centered predictor on Y
-model.centered<-lm(dat$______ ~ dat$______.center)
-summary(model.centered)
-
-#centered models:
-m1.cent<-lm(dat$Y ~ dat$X.center 
-            + dat$M)
-summary(m1.cent)
-
-m2.cent<-lm(dat$Y ~ dat$X.center 
-            + dat$M
-            + (dat$X.center*dat$M))
-summary(m2.cent)
-
-#compare models
-anova(m1.cent, m2.cent)
-
-#Work on tables:
-#In another working document (because incomplete)
 ```
 
-Graph results of moderation analysis
+(2) Explanation: 
+The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions, respectively, in Study 3.
+Note that at the bottom of the table is also the chi-square statistic, p-value and effect size (phi) for the data, indicating a medium-sized effect of music condition on pen choice.
+The table also demonstrates that the frequency of choice in the Disliked Music condition was in the hypothesized direction: Subjects tended to choose the non-advertised pen when made to listen to disliked music in an advertisement.
+Please note that the data represented above follows the exclusion criteria set forth in the published article.
+Specifically, any subjects who had participated in a prior version of the study were excluded (two subjects).
+In addition, 19 subjects were excluded for their so-called "deviant music evaluations".
+These subjects were foundd to either somewhat dislike the "liked music" (music attiude score below 3) or somewhat like the "disliked music" (music attitude score above 3).
 
-```{r, echo=FALSE}
-##Scatterplots for add on to study graphs 
-graph.simple = ggplot(dat, aes(x = , y = )) 
-graph.simple + geom_smooth(method = "") +
-  geom_point() +
-  ggtitle("") +
-  ylab("") +
-  xlab("")
+(3) Code for analyses & table:
 
-graph.moderator = ggplot(dat, aes(x = X.center, y = Y, colour = M)) 
-graph.moderator + geom_smooth(method = "lm") +
-  geom_point() +
-  ggtitle("") +
-  ylab("") +
-  xlab("")
+```{r eval= FALSE}
+
+# Load data
+dat <- read.csv("GORN_study3.csv", header = TRUE)
+dat <- tbl_df(dat)
+#head(dat)
+#View(dat)
+
+# Designate factors:
+dat$Groep <- as.factor(dat$Groep)
+dat$music <- as.factor(dat$music)
+dat$chose_advertised_pen <- as.factor(dat$chose_advertised_pen)
+
+# Filter out 2 excluded participants who accidentily took study twice in the paper:
+dat_e <- dat %>%
+  filter(excluded == 0)
+#dat_e
+#View(dat_e)
+
+## Analyses on ENTIRE sample:
+
+# Test whether music condition is independent of pen choice:
+# (1 == liked music, 2 == disliked music)
+# (0 == not chosen, 1 == chosen)
+tbl = table(dat_e$music, dat_e$chose_advertised_pen) 
+tbl
+
+# Chi-Square, no correction, no simulation:
+cs1 <- chisq.test(tbl, correct = FALSE)
+
+# Power analysis -- Find the power to detect .35 effect size reported in paper:
+pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)
+
+# Power analysis -- Find the effect size for a test with .8 sensitivity:
+pwr.chisq.test(w = NULL, N = 91, df = 1, sig.level = 0.05, power = .8)
+
+# Analyses on SUBSETTED sample:
+
+# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:
+
+# Find Cronbach's Alpha for music attitudes scale (for comparison with article):
+#dat_music <- dat_e %>%
+#  select(att_muz1, att_muz2, att_muz3)
+#View(dat_music)
+#alpha(dat_music, na.rm = TRUE, delete=TRUE)
+
+# Find mean attitudes for each music condition (for comparison with article): 
+#dat_e %>%
+#  group_by(music) %>%
+#  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))
+
+# Add mean attitude column to dataframe:
+dat_e <- dat_e %>%
+  mutate(avg_att_muz = (att_muz1 + att_muz2 + att_muz3) / 3)
+#View(dat_e)
+
+# Check those means (for comparison with article):
+#dat_e %>%
+#  group_by(music) %>%
+#  summarise(avg = mean(avg_att_muz))
+
+# Exclude when average attitude > 3 in disliked cond. or average attitude <3 for liked cond. (1 == liked music, 2 == disliked music)
+dat_egood <- dat_e %>%
+  filter(music == 1 & avg_att_muz > 3 | music == 2 & avg_att_muz < 3)
+#View(dat_egood)
+
+## Redo Chi-Square with subsetted data:
+
+# Test whether music condition is independent of pen choice:
+# Create 2x2 contingency table of frequencies - pen choice by music condition
+tbl2 = table(dat_egood$music, dat_egood$chose_advertised_pen) 
+tbl2
+
+# Chi-Square, no correction, no simulation:
+cs2 <- chisq.test(tbl2, correct = FALSE)
+tidy(cs2)
+
+# Power analysis -- Find the power to detect .35 effect size reported in paper:
+pwr.chisq.test(w = .35, N = 72, df = 1, sig.level = 0.05, power = NULL)
+
+# Power analysis -- Find the effect size for a test with minimum of .8 sensitivity:
+pwr.chisq.test(w = NULL, N = 72, df = 1, sig.level = 0.05, power = .8)
+
+# Confidence Intervals (not replicated from paper):
+#upper (95%)
+#CI95_up <- qchisq(.95, df = 1)
+#lower (5%)
+#CI95_low <- qchisq(.05, df = 1)
+
+## Replicate Table: Frequency table & chi-square statistic of subsetted data
+# (replicate "Experiment 3" portion of the table from article)
+
+# Generate count and proportion (percent) tallies for replicating the table:
+# Amongst those in Liked Music condition:
+dat_egoodLike <- dat_egood %>%
+  filter(music == 1)
+dat_egoodLike %>%
+  group_by(chose_advertised_pen) %>%
+  summarise(n = n(),
+            percent = n / nrow(dat_egoodLike) * 100)
+
+# Amongst those in Disliked Music condition:
+dat_egoodDislike <- dat_egood %>%
+  filter(music == 2)
+dat_egoodDislike %>%
+  group_by(chose_advertised_pen) %>%
+  summarise(n = n(),
+            percent = n / nrow(dat_egoodDislike) * 100)
+
+# Generate table:
+Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
+Disliked_Music <- c("8(23%)","27(77%)", "")
+Condition <- c("AdvertisedPen", "NonAdvertisedPen", "Chi-Square")
+Freq_Table = cbind(Condition, Liked_Music, Disliked_Music)
+stargazer(Freq_Table, type = "text", title = "Study 3: Frequencies of Pen Choice for Each Conditon & Chi-Square")
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the table.
+Further, the "eval = FALSE" parameter was added to the top code chunk to prevent printing of the code.
